---
title: "p8105_hw1_sp3903"
output: github_document
---

# Problem 1

## Creating a dataframe
### Loading tidyverse
```{r}
library(tidyverse)
```

### Creating a dataframe
```{r}
data_frame = tibble(
  x = rnorm(10),
  vec_logical = x > 0,
  vec_char = c("a","b","c","d","e","f","g","h","i","j"),
  vec_factor = factor(c("low","moderate","high","low","moderate","high","low","moderate","high","low"))
)
```

### Finding the means
```{r}
library(tidyverse)
mean(pull(data_frame, x))
mean(pull(data_frame, vec_logical))
mean(pull(data_frame, vec_char))
mean(pull(data_frame, vec_factor))
```

## Means descriptions
* The mean for the variables x and vec_logical run without errors because they are numeric.
* The mean for the variables vec_char and vec_factor do not work because they are character variables. 

## Converting charactor and factor variables to numeric
```{r, eval = FALSE}
as.numeric(pull(data_frame, vec_char))
as.numeric(pull(data_frame, vec_factor))
```

When converting the vec_char variable to numeric, there is a NA's introduced by coercion warning message. 
When converting the vec_factor to numeric, R produces a mean by adding values to each of the three factors. 
This provides context as to how R converts factors into numeric values. 

# Problem 2
### Loading Package
```{r}
data("penguins", package = "palmerpenguins")
```

### Dataset description
* The data in this dataset include the following variables: `r variable.names(penguins)`.
* The size of the dataset  `r nrow(penguins)` rows and `r ncol(penguins)` columns.
* The range of flipper length is (`r range(penguins$flipper_length_mm, na.rm = TRUE)`) mm.
* The mean flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm.
* The variance of the flipper length is `r var(penguins$flipper_length_mm, na.rm = TRUE)` mm.

## Scatterplot
```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
```

```{r, echo=FALSE}
ggsave("results/penguins.pdf", height = 4, width = 6)
```

This scatterplot displays the flipper length in mm by the bill length in mm. The colors indicate the species of penguins. 






