---
title: "p8105_hw1_sp3903"
output: github_document
---

# Problem 1

##Creating a dataframe
```{r}
library(tidyverse)
```

Instructions:
Create a data frame comprised of:
* a random sample of size 10 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 10
* a factor vector of length 10, with 3 different factor “levels”

```{r}
data_frame = tibble(
  x = rnorm(10),
  vec_logical = x > 0,
  vec_char = c("a","b","c","d","e","f","g","h","i","j"),
  vec_factor = factor(c("low","moderate","high","low","moderate","high","low","moderate","high","low"))
)
```

##Finding the Means

Instructions
*Try to take the mean of each variable in your dataframe. What works and what doesn’t?

```{r}
library(tidyverse)
mean(pull(data_frame, x))
mean(pull(data_frame, vec_logical))
mean(pull(data_frame, vec_char))
mean(pull(data_frame, vec_factor))
```

The mean for the variables x and vec_logical work because they are numeric.
The mean for the variables vec_char and vec_factor do not work because they are character variables. 

##Penguins Dataset Description

```{r}
data("penguins", package = "palmerpenguins")
```

* The data in this dataset include the following variable: `head(penguins, 1)`.
* The size of the dataset `skimr::skim(penguins)`.
* The mean flipper length is `mean(flipper)`.

#scatterplot
```{r}
ggplat(pengin_plot, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
```

```{r, echo=FALSE}
ggave("results/penguin_plot", height = 4, width = 4)
```







